---
title: "Lab 00 - Hello IDS!"
author: "Matteo Smirne"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Matteo", "Duncan", "Barney", 
           "Euan", "Romi", "Karan"),
  github_username = c("MatteoSmirne", " Djones2334", "bmccreery", 
                      "euanriach", "romikaushik", "karan-s06"), 
  colour = c("blue", "green", "green", 
             "blue", "green", "purple"),
  hobby = c("Formula 1", "MMA", "Motorsport", 
            "Football", "swimming", "badminton"),
  favourite_number = c(9, 1, 4, 7, 9, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


#each team members github username on the x axis and their favourite number on the y axis

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github username", 
          y = "favourite number",
          title = "Team members favourite number")
```

#allows you to modify axis labels

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
